### 2016-09-18 image_setup.tex
minor changes

% Define variable]
\begin{lstlisting}[]
$ export URL="http://kom.aau.dk/project/TuneSCode/raspi/"
$ export IMAGE="2016-05-27-raspbian-jessie-lite"
$ export WORKDIR="${HOME}/Raspbian"
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
\todot{change to zenodo link above}

@@

% Download and unpack image
\begin{lstlisting}[]
$ mkdir -p ${WORKDIR}
$ cd ${WORKDIR}
$ wget ${URL%/*}/${IMAGE}.zip
$ unzip ${IMAGE}.zip
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

% Get the configuration files that are compressed in a remote server
\begin{lstlisting}[]
$ wget ${URL%/*}/rasp_config.zip
$ unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
Archive:  rasp_config.zip
   creating: ${ROOTDIR}/home/pi/rasp_config/
  inflating: ${ROOTDIR}/home/pi/rasp_config/nodes.csv
  inflating: ${ROOTDIR}/home/pi/rasp_config/set_hostname
  inflating: ${ROOTDIR}/home/pi/rasp_config/main
  inflating: ${ROOTDIR}/home/pi/rasp_config/update_rasp_config
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

In our case as the testbed administrator for presenting the procedure, we want
to fetch all our configuration scripts in
\texttt{\$\{URL\%/*\}/raspi\_config.zip}. The update script
\textit{automatically} downloads all the required configuration files in
\texttt{rasp\_config.zip} file from a remote location. This is the same that
we manually did earlier to get our files but this will be made in an
automated way after booting up the system. This script content is:

>>>>

% Define variable]
\begin{lstlisting}[]
$ export URL="https://zenodo.org/record/154328/files/"
$ export IMAGE="2016-05-27-raspbian-jessie-lite"
$ export WORKDIR="${HOME}/Raspbian"
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
\todot{change to zenodo link above}

@@

% Download and unpack image
\begin{lstlisting}[]
$ mkdir -p ${WORKDIR}
$ cd ${WORKDIR}
$ wget ${URL%/}/${IMAGE}.zip
$ unzip ${IMAGE}.zip
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

% Get the configuration files that are compressed in a remote server
\begin{lstlisting}[]
$ wget ${URL%/}/rasp_config.zip
$ unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
Archive:  rasp_config.zip
   creating: ${ROOTDIR}/home/pi/rasp_config/
  inflating: ${ROOTDIR}/home/pi/rasp_config/nodes.csv
  inflating: ${ROOTDIR}/home/pi/rasp_config/set_hostname
  inflating: ${ROOTDIR}/home/pi/rasp_config/main
  inflating: ${ROOTDIR}/home/pi/rasp_config/update_rasp_config
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

In our case as the testbed administrator for presenting the procedure, we want
to fetch all our configuration scripts in
\texttt{\$\{URL\%/\}/raspi\_config.zip}. The update script
\textit{automatically} downloads all the required configuration files in
\texttt{rasp\_config.zip} file from a remote location. This is the same that
we manually did earlier to get our files but this will be made in an
automated way after booting up the system. This script content is:
